\mbox{Verifying Imperative Higher-Order Programs}

### 2009-10-07 papers/esop2010/main.tex
go

\author{Johannes Kanig\inst{1,}\inst{2} \and Jean-Christophe
Fill\^atre\inst{2,}\inst{1}}
\institute{
INRIA Saclay - Île-de-France, ProVal, Orsay, F-91893 \and
 LRI, Univ Paris-Sud, CNRS, Orsay, F-91405
}
%TODO explain somewhere the correspondence store type <-> map, effect variable
%<-> domain, region <-> key

\maketitle

@@

\section{The general picture and a motivating example}
\label{sec:genpic}

@@

\section{A programming language for specification}
\label{sec:syntax}

%TODO  notion of substitution - correspondence χ κ
\subsection{Syntax}
\begin{figure}[tpb]
\begin{eqnarray*}
  x & & \text{Program Variables}\\
  α & & \text{Type Variables}\\
  e & & \text{Effect Variables}\\
  ρ & & \text{Region Variables}\\
  χ &::=& α \sep e \sep ρ \\
  t,p,q &::=& x~[\alist{κ}] \sep λx:τ.t \sep \recml~f~(x:τ).\{p\}t\{q\} \sep t~t\sep \\ 
  & & \letml~ x~[\alist{χ}] = t~\inml~t \sep \ifml~t~\thenml~t~\elseml~t\\
  τ &::=& α \sep τ -> τ \sep τ ->^ε τ \sep τ \times τ \sep τ~\refml_ρ \sep
  \efft{ε} \\
  ε &::=& (ρ \sep e)*\\
  κ &::=& τ \sep ε \sep ρ
\end{eqnarray*}
  \caption{Syntax}
  \label{fig:syntax}
\end{figure}

@@

\subsection{Alias restriction}

@@

@@

\subsection{A more powerful memoization function}

@@

\subsection{All examples - an overview}

A prototype implementation of the presented system, called ``\who'',
 is freely available~\cite{KanigFilliatre09wml}%TODO \footnote
. It implements the
described language with type, region and effect polymorphism, higher-order
logic and store types in the logic. It takes as an input a fully annotated
program and outputs proof obligations which have to be proved to guarantee the
correctness of the program with respect to its specification. Currently, only
output to the interactive proof assistant Coq has been implemented. Our logic
is a subset of Coq's, so the translation is particularly simple.
The implementation consists of less than 3000 lines of \ocaml\ code, including
a limited form of type and effect inference.

>>>>

\author{Johannes Kanig\inst{1,}\inst{2} \and Jean-Christophe
Fill\^atre\inst{2,}\inst{1}}
\institute{
INRIA Saclay - Île-de-France, ProVal, Orsay, F-91893 \and
 LRI, Univ Paris-Sud, CNRS, Orsay, F-91405
}
\maketitle

@@

\section{The General Picture and a Motivating Example}
\label{sec:genpic}

@@

\section{A Programming Language for Specification}
\label{sec:syntax}

\subsection{Syntax}
\begin{figure}[tpb]
\begin{eqnarray*}
  x & & \text{Program Variables}\\
  α & & \text{Type Variables}\\
  e & & \text{Effect Variables}\\
  ρ & & \text{Region Variables}\\
  χ &::=& α \sep e \sep ρ \\
  t,p,q &::=& x~[\alist{κ}] \sep λx:τ.t \sep \recml~f~(x:τ).\{p\}t\{q\} \sep t~t\sep \\ 
  & & \letml~ x~[\alist{χ}] = t~\inml~t \sep \ifml~t~\thenml~t~\elseml~t\\
  τ &::=& α \sep τ -> τ \sep τ ->^ε τ \sep τ \times τ \sep τ~\refml_ρ \sep
  \efft{ε} \\
  ε &::=& (ρ \sep e)*\\
  κ &::=& τ \sep ε \sep ρ
\end{eqnarray*}
  \caption{Syntax}
  \label{fig:syntax}
\end{figure}

@@

\subsection{Alias Restriction}

@@

\subsection{A Simple Memoization Function}

@@

\subsection{A More Powerful Memoization Function}

@@

\subsection{All Examples - An Overview}

A prototype implementation of the presented system, called ``\who'', is freely
available~\cite{KanigFilliatre09wml}\footnote{It is available at
\url{http://www.lri.fr/~kanig/who.html}.}. It implements the described
language with type, region and effect polymorphism, higher-order logic and
store types in the logic. It takes as an input a fully annotated program and
outputs proof obligations which have to be proved to guarantee the correctness
of the program with respect to its specification. Currently, only output to
the interactive proof assistant Coq has been implemented. Our logic is a
subset of Coq's, so the translation is particularly simple.  The
implementation consists of less than 3000 lines of \ocaml\ code, including a
limited form of type and effect inference.
